### 2014-11-13 implementation.tex
Fixed a few typos.

In the paper~\cite{cruz-ppdp14}, the LM virtual machine was measured and
compared against implementations of similar programs but written in other
languages. For instance, the Loopy Belief Propgation program was found to be around 2 times slower
than GraphLab, while the N Queens program was found to be around 10 to 15 slower
than a sequential C implementation. Some of those programs were also compared against
a Python implementations and LM faired fairly well. We measured
the impact of the coordination mechanisms implemented for the CLM
virtual machine on regular LM programs and saw very little to no degration.
Since we also performed general performance improvements, programs such as
PageRank and Greedy Graph Coloring now perform slightly better than before.

>>>>

In the paper~\cite{cruz-ppdp14}, the LM virtual machine was measured and
compared against implementations of similar programs but written in other
languages. For instance, the Loopy Belief Propagation program was found to be around 2 times slower
than GraphLab, while the N Queens program was found to be around 10 to 15 slower
than a sequential C implementation. Some of those programs were also compared against
a Python implementations and LM faired fairly well. We measured
the impact of the coordination mechanisms implemented for the CLM
virtual machine on regular LM programs and saw very little to no degradation.
Since we also performed general performance improvements, programs such as
PageRank and Greedy Graph Coloring now perform slightly better than before.
